Turbo fast no compromise gravitational wave parameter estimation

### 2023-01-08 src/tex/ms.tex
Add pp Plot caption, all hail github copilot

\begin{figure}
    \script{ppplots.py}
    \includegraphics[width=0.99\linewidth]{figures/ppplot.pdf}
    \caption{Result of 1000 injections drawn from the 16 seconds prior.}
    \label{fig:ppplot}
    \end{figure}

>>>>

\begin{figure}
    \script{ppplots.py}
    \includegraphics[width=0.99\linewidth]{figures/ppplot.pdf}
    \caption{Cumulative distribution of the quantile of which the true value
    lies for each marginalized distribution. The shadow band denotes the 95\%
    credible interval drawn from a uniform distribution with the same number of
    events as the injection campaign. The legend shows the p-values for each
    marginalized distribution.}
    \label{fig:ppplot}
    \end{figure}
